Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex
Accidentally deleted GitHub

The second part of the project is motivated by a desire to test the feasibility of using the small Raspberry Pi Linux computer as a platform for capturing and processing images of license plates. Because the Raspberry Pi is inexpensive (\$25-\$35 depending on the model), it could be useful in a wide variety of applications that require accurate license plate recognition. For now our web application will simply list the license plate numbers for site administrators to view, but we envision that this monitoring system may eventually be used by the campus parking department to detect when vehicles have entered lots without parking passes.

The goal of this project is to work with the ACMx group to create and deploy the system in two parking lots on campus by the end of the semester. See section 2.7 for information about the deployment. The system itself will consist of several subsystems, which are described in detail in section 2.

@@

\section{Project Overview and Methods}
\begin{figure}
\begin{center}
\includegraphics[width=4.5in]{architecture}
\end{center}
\caption{Overall System Architecture}
\label{fig:system}
\end{figure}
This project is partially an extension of the ACMx SmartLots project. The system consists of several components, each of which will is either an extension of a current SmartLots system or an entirely new subsystem that has been integrated into the existing system. Figure \ref{fig:system} shows the overall architecture of our system. The system relies on three main components:
\begin{enumerate}
\item Detection Subsystem,
\item Central Base Station, and
\item Server.
\end{enumerate}

@@

\section{Results}
\subsection{ALPR Results}
Three data sets were run through each ALPR system. In each case, Intrada ALPR was able to recognize at least double as many plates as OpenALPR.

@@

\subsubsection{Validating and Adjusting Lot Capacity Data}
We expect that our first deployment of this system may not be 100\% accurate at detecting all vehicles that enter and exit lots. Therefore, we would like to create a system to periodically collect overhead images of the parking lots from a camera mounted on the base station Raspberry Pi. These images would serve as a visual representation of how many cars were actually in the parking lot at the time the image was taken. If this feature is implemented, administrators will be able to periodically compare the overhead images to the collected data from the sensor network to make sure the numbers being computed by the system accurately represent the car counts of the lots. A page would be added to the web interface to allow administrators to pull up the image for any lot with an overhead camera and see the numbers for that lot right next to the image. If any discrepancies are found, the administrator would be able to overwrite the count in the database to reflect reality. Such an interface would be useful in helping to calibrate the system. For example, if the sensors consistently report less cars in the lot than the image shows, they can be fine-tuned to make sure fewer cars slip through unnoticed. Another improvement to work in this area could include an automated version of this process, where a computer program could compare the overhead images to the sensed data and make any necessary corrections to the car count in the database.

>>>>

The second part of the project is motivated by a desire to test the feasibility of using the small Raspberry Pi Linux computer as a platform for capturing and processing images of license plates. Because the Raspberry Pi is inexpensive (\$25-\$35 depending on the model), it could be useful in a wide variety of applications that require accurate license plate recognition. Currently our web application simply lists the license plate numbers for site administrators to view, but we envision that this monitoring system may eventually be used by the campus parking department to detect when vehicles have entered lots without parking passes. The system itself will consist of several subsystems, which are described in detail in section 2.

@@

\section{Project Overview and Methods}

\begin{figure}
\begin{center}
\includegraphics[width=4.5in]{architecture}
\end{center}
\caption{Overall System Architecture}
\label{fig:system}
\end{figure}

This project is partially an extension of the ACMx SmartLots project. The system consists of several components, each of which will is either an extension of a current SmartLots system or an entirely new subsystem that has been integrated into the existing system. Figure \ref{fig:system} shows the overall architecture of our system. The system relies on three main components:
\begin{enumerate}
\item Detection Subsystem,
\item Central Base Station, and
\item Server.
\end{enumerate}

@@

\section{Results}
\subsection{ALPR Results}
Three data sets were run through each ALPR system. In each case, Intrada ALPR was able to recognize at least twice as many plates as OpenALPR.

@@

\subsection{Validating and Adjusting Lot Capacity Data}
We expect that our first deployment of this system may not be 100\% accurate at detecting all vehicles that enter and exit lots. Therefore, we would like to create a system to periodically collect overhead images of the parking lots from a camera mounted on the base station Raspberry Pi. These images would serve as a visual representation of how many cars were actually in the parking lot at the time the image was taken. If this feature is implemented, administrators will be able to periodically compare the overhead images to the collected data from the sensor network to make sure the numbers being computed by the system accurately represent the car counts of the lots. A page would be added to the web interface to allow administrators to pull up the image for any lot with an overhead camera and see the numbers for that lot right next to the image. If any discrepancies are found, the administrator would be able to overwrite the count in the database to reflect reality. Such an interface would be useful in helping to calibrate the system. For example, if the sensors consistently report less cars in the lot than the image shows, they can be fine-tuned to make sure fewer cars slip through unnoticed. Another improvement to work in this area could include an automated version of this process, where a computer program could compare the overhead images to the sensed data and make any necessary corrections to the car count in the database.
